An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-21 neurips-19/poly-embed.tex
Adding refs and removing discussion of embedding dimension

%\title{An Embedding Framework for Consistent Polyhedral Surrogates}
\title{Consistent Polyhedral Surrogates via Embeddings}
%\title{Convex Surrogates via Polyhedral Losses}
\author{%
 Jessica Finocchiaro\raf{Jessie?} \\
 \texttt{jessica.finocchiaro@colorado.edu}\\
 CU Boulder
 \And
 Rafael Frongillo\\
 \texttt{raf@colorado.edu}\\
 CU Boulder
 \And
 Bo\\
 \texttt{bwag@colorado.edu}\\
 MSFT
}

@@

Convex surrogate losses are a central building block in machine learning for classification and classification-like problems.
A growing body of work seeks to design and analyze convex surrogates for given loss functions, and more broadly, understand when such surrogates can and cannot be found.
For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space~\cite{frongillo2015elicitation,  ramaswamy2016convex}.
Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\cite{bartlett2008classification, yuan2010classification, ramaswamy2016convex, ramaswamy2018consistent}.
Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well-understood.

We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
Specifically, we say a convex surrogate $L$ embeds a discrete loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
If additionally there exists a ``separated'' link function which maps approximately $L$-optimal reports to $\ell$-optimal reports, this condition is known to produce $\ell$-calibrated surrogates~\cite{agarwal2015consistent}.
Common examples which follow this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.

@@

We go on to initiate a study of \emph{embedding dimension}: the minimal dimension for a given discrete loss to be so embedded.
Our results give a complete characterization in the case of dimension 1; that is, real-valued surrogates.
We find that a discrete loss can be embedded in the real line if and only if it is order-sensitive, meaning there is an ordering of the predictions such that the loss increases as one moves away from the correct prediction.
We show further that order-sensitivity characterizes the existence of \emph{any} real-valued convex surrogate, implying that embeddings lose no generality.
We conclude with preliminary results in higher dimensions and other future directions.

\subsection{Related works}
Convex surrogates have been formalized and investigated in a variety of past work such as \cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification}, particularly in the context of 0-1 loss, distributions on just two outcomes, and support vector machines.
%  \cite{crammer2001algorithmic} is one of the first papers to present a convex surrogate for multiclass classification problems in the context of support vector machines.
%  They use the convex surrogate $L(\textbf{r},y) = (\max_{j\neq y} r_j - r_y + 1)_+$, where $\textbf{r}$ is a $n$-dimensional vector corresponding to the entire distribution, and $r_j$ is the $j^{th}$ component of \textbf{r}.
%
%  \cite{bartlett2006convexity} provides one of the most well-known formalizations of convex surrogates for properties on binary outcomes.
%  This work evaluates the risk bounds of convex surrogates and shows the sufficiency of convex surrogates such as logistic loss to replace the 0-1 loss for ease of optimization, and has inspired a line of research in the design of consistent surrogate losses for binary classification problems.
%  \jessiet{This is based on what I remember.  Couldn't find the free version (off the campus network) but also didn't look hard at all, since I'm guessing one of you two already knows this paper better than I do.}
%
%%  \cite{bartlett2008classification} studies the abstain property with $n=2$ and shows a variation of the hinge loss that is one convex surrogate that elicits the abstain property to two outcomes.
%
%  \cite{ramaswamy2012classification} discuss and formalize the notion of \emph{convex calibration} dimension for finite properties.
%  The concept they call convex calibration dimension is one notion of elicitation complexity discussion in this paper.
%  Denoted here by $\eliccvx(\gamma)$, convex calibration refers to the minimum dimension $d$ such that the property $\gamma$ can be indirectly elicited by a convex loss $L:\reals^d \to \reals^\Y_+$.
%
%  Most of the preliminary work on the construction of convex surrogate losses focuses on learning the mode in a binary classification problem.
  One of the first works formally studying convex surrogates beyond binary outcomes is~\cite{ramaswamy2018consistent}, who give an embedding of the \emph{abstain loss} into very few dimensions.
For the case of $\reals^2$ \jessiet{$\reals^2$ or $n \in \{3, 4\}$?}, we will show that no embedding can do better.
%  Rather than focusing on the mode, this paper proves bounds on the elicitation complexity of the abstain property.
%  They provide a consistent surrogate that elicits abstain with $\alpha = 1/2$ in $\ceil*{\log_2 n}$ dimensions. \jessiet{I don't like how much I'm talking about elicitation without the context.}
%  It remains unknown if this bound is tight, although in Conjecture~\ref{conj:abstain-tight}, we conjecture that it is, at least from the perspective from ``embedding''.
%  If true, then we will need new approaches in order to indirectly elicit the abstain property by a convex surrogate for any dimension lower than $\ceil*{\log_2 n}$.
%
%  \cite{agarwal2015consistent} introduces the notion of a \emph{calibrated property}, which is very similar to our \emph{surrogate property} that we elicit by a convex surrogate in lieu of directly eliciting a finite property.
%  However, they do not consider properties to be set-valued, leading to subtle differences in the property values for some distributions.
%  Additionally, most of their results focus on linear properties. \jessiet{is there a relationship between linear and orderable properties?  If not, we can probably remove this statement.}
%
  \citet{agarwal2015consistent} and~\citet{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
  These works are generally not directly comparable to our results, as they do not consider the embedding method. \jessiet{In what sense do they not consider embedding?  The formalism we present?  They intuitively embed into the reals, but I don't remember if they focus on polyhedral losses}
  However, we will mention relevant results inline.
%  In~\cite{ramaswamy2016convex}, the authors introduce a new method of obtaining upper bounds on elicitation complexity called the \emph{Feasible Subspace Dimension}.
%  This method uses local information about distributions in a property in order to find bounds on the convex elicitation complexity of a property.
%  For example, Feasible Subspace Dimension can be used to find a tight bound on $\eliccvx$(mode), but does not reveal a tight bound for the abstain property discussed later.
%  This suggests that the bound on $\eliccvx$(abstain) must be found using more \emph{global} information about the property.
%  We discuss this in Section~\ref{sec:general-dimensions}, showing previously unknown necessary conditions for embedding finite properties.

@@

Let $\Y$ be a finite outcome (label) space, and throughout let $n=|\Y|$.
The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
\jessie{Given labeled data of the form $(x,y)$, we abstract away the data input and consider the conditional probabilities $p(Y|X)$, and this is what we denote as $p_y$.}
\jessiet{Do we want to go into the detail of thinking of $p_y$ as $p(Y|X)$ in finite data}

\raf{Important TODO: we use $\reals^\Y$ sometimes and $\reals^\Y_+$ other times; ideally both $+$, but we need to see what we can prove...  I know this is a key detail for polyhedral losses, to ensure the inf is always attained.}
\jessiet{If the convex loss is bounded from below by $M$, we can say $\reals^\Y_+$ WLOG since $L$ elicits $\Gamma$ implies $(L +c)$ elicits $\Gamma$ for any constant $c$-- in particular, $M$.  We might also assume our discrete loss is nonnegative?}

We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\Delta(\Y)$.
Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$.
(A generic loss be written $L:\R\to\reals^\Y$.)
We write expected loss of report $r$ when $Y \sim p$ as $\inprod{p}{L(r)}$.
The \emph{Bayes risk} of a loss $L:\R\to\reals^\Y$ is the function $\risk{L}:\Delta(\Y)\to\reals$ given by $\risk{L}(p) := \inf_{r\in\R} \inprod{p}{L(r)}$; naturally for discrete losses we will write $\risk{\ell}$.

For example, 0-1 loss is a discrete loss with $\R = \Y = \{1,2,\ldots,n\}$ given by $\ell(r)_y = \Ind[r \neq y]$, and has Bayes risk $\risk{\ell}(p) = \max_{y\in\Y} p_y$.
Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.
\jessiet{Do we want to mention $r \to$ discrete reports and $u \to$ real reports?}

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex\jessiet{and bounded from below?}; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
%
\begin{definition}[Polyhedral loss]
  A loss $L: \reals^d \to \reals^{\Y}_+$ is a \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
\end{definition}
%
For example, the hinge loss is polyhedral, whereas logistic loss is not.

@@

\raf{How hinge fits in}
\jessie{Added the paragraphs below.}
To illustrate the idea of embeddings, we now look in detail at two key examples.
First, consider a binary classification problem on the outcomes $\{-1, +1\}$.
We know that both the hinge loss $L_{hinge}(u,y) := (1 - uy)_+$ and logistic loss $L_{logistic}(u,y) := \ln\left(1 + \exp(-uy)\right)$ are convex surrogates that are minimized in expectation by predicting the mode, as is 0-1 loss $\ell_{mode}(r,y) := \ones\{r\neq y\}$.
However, we say that hinge loss embeds the mode, while logistic loss does not.
\jessie{Come back to flesh this out if space?}

@@

\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
  \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
  \jessie{Stated in COLT Lemma 11 and Prop 12 (Lemma~\ref{lem:finite-full-dim} and Prop~\ref{prop:embed-trim} here), but I don't see us prove this in the original paper.}

  \jessie{The forward implication is a corollary of COLT Lemma 11}

  %Jessie's first attempt at a proof
  First, suppose $L$ embeds $\ell$, and fix $p \in \simplex$.
  We want to show for all $p \in \simplex$ that $\inf_{u\in\reals^d} L(u,p) = \min_{r \in \R} \ell(r, p)$.
  Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
  Then
  \begin{align*}
  \inf_u L(u,p) = \min_{r \in \R} L(\varphi(r), p) = \min_{r \in \R} \ell(r, p)
  \end{align*}
   first by the case assumption and then by the definition of embedding.
  Now in the second case, if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
  Therefore, $r \in \argmin_r' \ell(r', p) \implies \varphi(r) \not \in \argmin_u L(u,p)$ which contradicts the assertion that $L$ embeds $\ell$.

  \jessie{Not sure on this one, just FYI.  I think it's a corollary of COLT Prop 12, now Prop~\ref{prop:embed-trim}.}
  Now, to see that $\risk{\ell} = \risk{L} \implies L$ embeds $\ell$, consider $F$ to be the set of facets of the surface of $\risk{L}$.
  For each facet $f \in \F$, we know by nonredundancy that there is some $p \in \inter{f}$ so that $\risk{L}$ is differentiable at $p$.
  Moreover, by Frongillo and Kash~\cite[Theorem 2?]{frongillo2014general} \jessie{Check ref} we know that both $\ell$ and $L$ have a unique minimizer at $p$, and since the subgradients of the risks are the same (by their equality), we know the minimizers of the losses are also the same, up to relabeling the reports via a bijection.
  Therefore, we can see that $L$ embeds $\ell$, as $L(\varphi(r),y) = \ell(r,y)$ for all $r\in\R$ and $y \in \Y$.
  \jessie{Incomplete...?}

%  Now let us show that $\risk{L} = \risk{\ell} \implies L$ embeds $\ell$.
%  Let $F$ be the set of facets in $\risk{\ell}$.
%  For each $f \in F$, there is some $p \in \inter{f}$ so that $\risk{L}(p) = \risk{\ell}(p)$ is differentiable, and so the loss $L$ must then be uniquely defined.
%  \jessie{This is my interpretation of your note, but I don't see how this proves the existence of an embedding.  My inclination is to show there's the ``stripped'' loss that we embed ($\varphi(u) = u$) and for any bijection $\phi$, we can see that $\ell$ can be modified to $\ell^\phi$ so that $\risk{\ell} = \risk{\ell^\phi}$, and $L$ also embeds $\ell^\phi$ with $\varphi(r) = \phi(r)$.  Does that make sense?}

@@

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  \jessie{My attempt below}
  For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
  By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral. \jessie{Need to prove? Stated as fact in proof of COLT Prop 12...}
  Therefore, $\risk{L}$ is polyhedral.

  For the reverse implication, suppose $\risk{L}$ is polyhedral.
  For each facet $f \in F$ of $\risk{L}$, consider the report $u_f = \arginf_{u'} L(u', p)$ for some $p \in \inter f$.
  (Note that $u_f$ will be unique and the same regardless of the choice of $p\in \inter f$, since $\risk{L}$ is differentiable here.)
  Since $\risk{L}$ has a finite set of facets, the set $\R = \{u_f\}_{f \in F}$ is finite.
  Now define the discrete loss $\ell:\R \to \Y$ by $\ell(r,y) = L(r,y)$.

  To see that $L$ embeds this discrete $\ell$, consider the embedding function to be the identity for all $r \in \R$.
  By Proposition~\ref{prop:embed-bayes-risks}, it is sufficient to show $\risk{L} = \risk{\ell}$.
  For all $p \in \simplex$, we observe
  \begin{align*}
  	\risk{L}(p) = \inf_{u \in \reals^d} L(u,p) = \min_{r \in \R} L(r,p) = \min_{r \in \R} \ell(r, p) = \risk{\ell}(p)
  \end{align*}
  Note that the second equality holds because for every $p \in \simplex$, we know there is some $r \in \R$ such that $r \in \arginf_u L(u,p)$ by closure of subgradient sets, and thus the loss values are the same, regardless of if we restrict to $\R$ or stay in $\reals^d$.
  Thus, $L$ embeds the discrete $\ell$ as constructed by Proposition~\ref{prop:embed-bayes-risks}.

  \raf{Just take the discrete reports to be the facets, and use the Bayes risk result.}
\end{proof}

@@

\begin{theorem}\label{thm:poly-embeds-discrete}
  Every polyhedral loss $L$ embeds a discrete loss.
\end{theorem}
\begin{proof}
  We merely show $L$ polyhedral $\implies$ $\risk{L}$ polyhedral, and apply Proposition~\ref{prop:embed-risk-poly}.
  \raf{Not sure how trivial this is, but it's definitely true.  I suspect it has a very short proof.}
  \jessie{$L(u,p)$ polyhedral in $\reals^d$ implies $L^*(0,p) = -\risk{L}(p)$ polyhedral in $\simplex$ implies $\risk{L}$ polyhedral.
  Now we can apply Proposition~\ref{prop:embed-risk-poly} to observe the result.}

@@

\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
  Every discrete loss $\ell$ is embedded by a polyhedral loss.
\end{theorem}
\begin{proof}
  \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
  \jessie{Might try tonight without properties?}
\end{proof}

@@

\raf{Copied}
... given by Ramaswamy et al.~\cite{ramaswamy2018consistent}.
In their work, they provide a consistent, polyhedral \jessie{?} surrogate for the abstain loss $\ell_{abs_{\alpha}}:[n] \cup \{a\} \to \reals$ defined:
\begin{align}\label{eq:abstain}
\ell_{abs_{\alpha}}(r,y) := \begin{cases}
0 & r = y\\
\alpha & r = a\\
1 & otherwise
\end{cases}
\end{align}
Here, the report $a$ corresponds to ``abstaining'' from voting if the outcome of any outcome is not likely enough to occur.

The surrogate provided by Ramaswamy et al.~\cite{ramaswamy2018consistent} for $\alpha = 1/2$ embeds the $n$ outcomes into the $n$ vertices of the $\ceil{\log_2(n)}$-dimensional hypercube (vertices in $\{\pm 1\}^n$), and embeds the abstain point at the origin.
They go on to show consistency and provide a \jessie{which type?} link function from their surrogate to $\ell_{abs_{1/2}}$.

@@

Yang and Koyejo~\cite{yang2018consistency} prove the inconsistency of a family of polyhedral surrogates for the top-$k$ classification problem.
To illustrate our framework, we show how to simplify their arguments using embeddings.

The top $k$ classification problem takes as input a vector $r \in \R = \{r \in \{0,1\}^n \text{ such that } |r| = k\}$, \raf{mixing sets and indicators here, unless you mean $\|r\|_1$} and observes outcome $y \in [n]$

We say the top-$k$ loss $\ell_{top-k}:\R \to \reals$ is
\begin{align}
\ell_{top-k}(u,y) = \begin{cases}
0 & u_y = 1\\
1 & \text{otherwise}
\end{cases}
\end{align}

@@

Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions.\raf{CITE; can't remember which}
In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.
One then defines a joint loss function, which is often merely a function of the set of mispredictions, meaning $\ell^g(r)_y = g(\{i \in [k] : r_i \neq y_i\})$ for some function $g:2^{[k]}\to\reals$.
In an effort to provide a general convex surrogate for these settings when $g$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce the \emph{Lov\'asz hinge}, which leverages the well-known convex Lov\'asz extension of submodular functions.
While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open, which we resolve negatively.

>>>>

\title{An Embedding Framework for Consistent Polyhedral Surrogates}
%\title{Consistent Polyhedral Surrogates via Embeddings}
%\title{Convex Surrogates via Polyhedral Losses}
\author{%
 Jessica Finocchiaro\raf{Jessie?} \\
 \texttt{jessica.finocchiaro@colorado.edu}\\
 CU Boulder
 \And
 Rafael Frongillo\\
 \texttt{raf@colorado.edu}\\
 CU Boulder
 \And
 Bo\\
 \texttt{bwag@colorado.edu}\\
 MSFT
}

@@

Convex surrogate losses are a central building block in machine learning for classification and classification-like problems.
A growing body of work seeks to design and analyze convex surrogates for given loss functions, and more broadly, understand when such surrogates can and cannot be found.
For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space~\cite{frongillo2015elicitation,  ramaswamy2016convex}.
Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\cite{bartlett2008classification, yuan2010classification, ramaswamy2016convex, ramaswamy2018consistent, zhang2018reject}.
Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well-understood.

We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
Specifically, we say a convex surrogate $L$ embeds a discrete loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
If additionally there exists a ``separated'' link function which maps approximately $L$-optimal reports to $\ell$-optimal reports, this condition is known to produce $\ell$-calibrated surrogates~\cite{agarwal2015consistent}.
Common examples which follow this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above. \jessiet{Really 0-2 loss, but that seems like an unimportant nuance.}

@@

\jessie{Take out this paragraph?}
We go on to initiate a study of \emph{embedding dimension}: the minimal dimension for a given discrete loss to be so embedded.
Our results give a complete characterization in the case of dimension 1; that is, real-valued surrogates.
We find that a discrete loss can be embedded in the real line if and only if it is order-sensitive, meaning there is an ordering of the predictions such that the loss increases as one moves away from the correct prediction.
We show further that order-sensitivity characterizes the existence of \emph{any} real-valued convex surrogate, implying that embeddings lose no generality.
We conclude with preliminary results in higher dimensions and other future directions.

\subsection{Related works}
Convex surrogates have been formalized and investigated in a variety of past work such as \cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification}, particularly in the context of 0-1 loss, distributions on just two outcomes, and support vector machines.
%  \cite{crammer2001algorithmic} is one of the first papers to present a convex surrogate for multiclass classification problems in the context of support vector machines.
%  They use the convex surrogate $L(\textbf{r},y) = (\max_{j\neq y} r_j - r_y + 1)_+$, where $\textbf{r}$ is a $n$-dimensional vector corresponding to the entire distribution, and $r_j$ is the $j^{th}$ component of \textbf{r}.
%
%  \cite{bartlett2006convexity} provides one of the most well-known formalizations of convex surrogates for properties on binary outcomes.
%  This work evaluates the risk bounds of convex surrogates and shows the sufficiency of convex surrogates such as logistic loss to replace the 0-1 loss for ease of optimization, and has inspired a line of research in the design of consistent surrogate losses for binary classification problems.
%  \jessiet{This is based on what I remember.  Couldn't find the free version (off the campus network) but also didn't look hard at all, since I'm guessing one of you two already knows this paper better than I do.}
%
%%  \cite{bartlett2008classification} studies the abstain property with $n=2$ and shows a variation of the hinge loss that is one convex surrogate that elicits the abstain property to two outcomes.
%
%  \cite{ramaswamy2012classification} discuss and formalize the notion of \emph{convex calibration} dimension for finite properties.
%  The concept they call convex calibration dimension is one notion of elicitation complexity discussion in this paper.
%  Denoted here by $\eliccvx(\gamma)$, convex calibration refers to the minimum dimension $d$ such that the property $\gamma$ can be indirectly elicited by a convex loss $L:\reals^d \to \reals^\Y_+$.
%
%  Most of the preliminary work on the construction of convex surrogate losses focuses on learning the mode in a binary classification problem.
  One of the first works formally studying convex surrogates beyond binary outcomes is~\cite{ramaswamy2018consistent}, who give an embedding of the \emph{abstain loss} into very few dimensions.
 For the case of $\reals^2$ \jessiet{$\reals^2$ or $n \in \{3, 4\}$?}, we will show that no embedding can do better. \jessiet{Take out this sentence?}

%  Rather than focusing on the mode, this paper proves bounds on the elicitation complexity of the abstain property.
%  They provide a consistent surrogate that elicits abstain with $\alpha = 1/2$ in $\ceil*{\log_2 n}$ dimensions. \jessiet{I don't like how much I'm talking about elicitation without the context.}
%  It remains unknown if this bound is tight, although in Conjecture~\ref{conj:abstain-tight}, we conjecture that it is, at least from the perspective from ``embedding''.
%  If true, then we will need new approaches in order to indirectly elicit the abstain property by a convex surrogate for any dimension lower than $\ceil*{\log_2 n}$.
%
%  \cite{agarwal2015consistent} introduces the notion of a \emph{calibrated property}, which is very similar to our \emph{surrogate property} that we elicit by a convex surrogate in lieu of directly eliciting a finite property.
%  However, they do not consider properties to be set-valued, leading to subtle differences in the property values for some distributions.
%  Additionally, most of their results focus on linear properties. \jessiet{is there a relationship between linear and orderable properties?  If not, we can probably remove this statement.}
%
  \cite{agarwal2015consistent} and~\cite{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
  These works are generally not directly comparable to our results, as they do not consider the embedding method. 
  Agarwal and Agarwal~\cite{agarwal2015consistent} also consider properties that are real-valued, rather than possibly set-valued as we do.
  However, we will mention relevant results inline.
%  In~\cite{ramaswamy2016convex}, the authors introduce a new method of obtaining upper bounds on elicitation complexity called the \emph{Feasible Subspace Dimension}.
%  This method uses local information about distributions in a property in order to find bounds on the convex elicitation complexity of a property.
%  For example, Feasible Subspace Dimension can be used to find a tight bound on $\eliccvx$(mode), but does not reveal a tight bound for the abstain property discussed later.
%  This suggests that the bound on $\eliccvx$(abstain) must be found using more \emph{global} information about the property.
%  We discuss this in Section~\ref{sec:general-dimensions}, showing previously unknown necessary conditions for embedding finite properties.

@@

Let $\Y$ be a finite outcome (label) space, and throughout let $n=|\Y|$.
The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
\jessie{Given labeled data of the form $(x,y)$, we abstract away the data input and consider the conditional probabilities $p(Y|X)$, and this is what we denote as $p_y$.}

\raf{Important TODO: we use $\reals^\Y$ sometimes and $\reals^\Y_+$ other times; ideally both $+$, but we need to see what we can prove...  I know this is a key detail for polyhedral losses, to ensure the inf is always attained.}

We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\Delta(\Y)$.
Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$.
(A generic loss will be written $L:\R\to\reals^\Y$.)
We write expected loss of report $r$ when $Y \sim p$ as $\inprod{p}{L(r)}$.
The \emph{Bayes risk} of a loss $L:\R\to\reals^\Y$ is the function $\risk{L}:\Delta(\Y)\to\reals$ given by $\risk{L}(p) := \inf_{r\in\R} \inprod{p}{L(r)}$; naturally for discrete losses we will write $\risk{\ell}$.

\jessie{In general, we shall denote discrete reports by $r \in \R$, and real-valued reports by $u \in \U$.}
For example, 0-1 loss is a discrete loss with $\R = \Y = \{1,2,\ldots,n\}$ given by $\ell(r)_y = \Ind[r \neq y]$, and has Bayes risk $\risk{\ell}(p) = \max_{y\in\Y} p_y$. \jessie{Isn't that the Score $G$?  Don't we want $\risk{\ell} = 1 - \min_{y \in \Y} p_y$?}
Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex \jessie{and bounded from below?}; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
%
\begin{definition}[Polyhedral loss]
  A loss $L: \reals^d \to \reals^{\Y}_+$ is a \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
\end{definition}
%
For example, the hinge loss is polyhedral, whereas logistic loss is not.

@@

\raf{How hinge fits in}
\jessie{Added the paragraph below.}
To illustrate the idea of embeddings, we now look in detail at two key examples.
First, consider a binary classification problem on the outcomes $\{-1, +1\}$.
Both the hinge loss $L_{hinge}(u,y) := (1 - uy)_+$ and logistic loss $L_{logistic}(u,y) := \ln\left(1 + \exp(-uy)\right)$ are convex surrogates that are minimized in expectation by predicting the mode, as is 0-1 loss $\ell_{mode}(r,y) := \Ind[r\neq y]$.
However, we say that hinge loss embeds the mode, while logistic loss does not.

To see this, $\inprod{p}{L_{logistic}(u)}$ has an infinite set of minimizers over $p \in \Delta_2$ that are mapped to two reports, $\pm 1$.
If the linked surrogate correctly minimizes $L$ in expectation, 
\jessie{Come back to flesh this out if space?}

@@

\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
\end{proof}

@@

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}

@@

\begin{theorem}\label{thm:poly-embeds-discrete}
  Every polyhedral loss $L$ embeds a discrete loss.
\end{theorem}
\begin{proof}
  We merely show $L$ polyhedral $\implies$ $\risk{L}$ polyhedral, and apply Proposition~\ref{prop:embed-risk-poly}.
  \raf{Not sure how trivial this is, but it's definitely true.  I suspect it has a very short proof.}

@@

\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
  Every discrete loss $\ell$ is embedded by a polyhedral loss.
\end{theorem}
\begin{proof}
  \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
\end{proof}

@@

\raf{Copied}
... given by Ramaswamy et al.~\cite{ramaswamy2018consistent}.
In their work, they provide a consistent, polyhedral surrogate for the abstain loss $\ell_{\abstain{\alpha}}:[n] \cup \{a\} \to \reals$ defined:
\begin{align}\label{eq:abstain}
\ell_{\abstain{\alpha}}(r,y) := \begin{cases}
0 & r = y\\
\alpha & r = a\\
1 & otherwise
\end{cases}
\end{align}
Here, the report $a$ corresponds to ``abstaining'' from voting if the outcome of any outcome is not likely enough to occur.

The surrogate provided by Ramaswamy et al.~\cite{ramaswamy2018consistent} for $\alpha = 1/2$ embeds the $n$ outcomes into the $n$ vertices of the $\ceil{\log_2(n)}$-dimensional hypercube (vertices in $\{\pm 1\}^n$), and embeds the abstain point at the origin.
They go on to show consistency and provide a \jessie{which type?} link function from their surrogate to $\ell_{\abstain{1/2}}$.

@@

Yang and Koyejo~\cite{yang2018consistency} prove the inconsistency of a family of polyhedral surrogates for the top-$k$ classification problem.
Using our embedding framework, we show how to simplify their arguments.

The top $k$ classification problem takes as input a vector $r \in \R = \{r \in \{0,1\}^n : |r| = k\}$, \raf{mixing sets and indicators here, unless you mean $\|r\|_1$} and observes outcome $y \in \{1,2,\ldots, n\}$.

We say the top-$k$ loss $\ell_{top-k}:\R \to \reals$ is
\begin{align}
\ell_{top-k}(r,y) = \begin{cases}
0 & r_y = 1\\
1 & \text{otherwise}
\end{cases}
\end{align}

@@

Many structured prediction settings can be thought of as making multiple predictions at once, with a loss function that jointly measures error based on the relationship between these predictions.\cite{hazan2010direct, gao2011consistency} \raf{CITE; can't remember which}
In the case of $k$ binary predictions, these settings are typically formalized by taking the predictions and outcomes to be $\pm 1$ vectors, so $\R=\Y=\{-1,1\}^k$.
One then defines a joint loss function, which is often merely a function of the set of mispredictions, meaning $\ell^g(r)_y = g(\{i \in [k] : r_i \neq y_i\})$ for some function $g:2^{[k]}\to\reals$.
In an effort to provide a general convex surrogate for these settings when $g$ is a submodular function, Yu and Blaschko~\cite{yu2018lovasz} introduce the \emph{Lov\'asz hinge}, which leverages the well-known convex Lov\'asz extension of submodular functions.
While the authors provide theoretical justification and experiments, consistency of the Lov\'asz hinge is left open, which we resolve negatively.
